Hydras \& Co.

### 2024-02-19 doc/chapter-primrec.tex
small corrections

Let us look at the proof that any constant $n$ of type \texttt{nat} has type (\texttt{PR 0})
(lemma  \texttt{const0\_NIsPR} of \texttt{primRec}). We carry out a proof by induction on $n$, the base case of which is already proven.
Now, let us assume $n$ is \texttt{PR $0$}, with $x:\texttt{PrimRec}\,0$ as a ``realizer''.
Thus we would like to compose this constant function with the unary successor function.

This is exactly the role of the instance \texttt{composeFunc 0 1} of the dependently typed
function \texttt{composeFunc}, as shown by the following lemma.

\vspace{4pt}
\input{movies/snippets/PrimRecExamples/compose01}

\vspace{4pt}
Here is a quite simple proof of \texttt{const0\_NIsPR}.

@@

We have already proven that \texttt{Nat.add} is primitive recursive. The following alternative proof, --- more detalled  ---, 
shows how to search and apply lemmas from
the \texttt{Ackermann} library.

Let us look for some lemma which could help to prove some 
recursive arithmetic binary function is primitive recursive.

>>>>

Let us look at the proof that any constant $n$ of type \texttt{nat} has type (\texttt{PR 0})
(lemma  \texttt{const0\_NIsPR} of \texttt{primRec}). We carry out a proof by induction on $n$, the base case of which is already proven.
Now, let us assume $n$ is \texttt{PR $0$}, and call $(x:\texttt{PrimRec}\,0)$ its ``realizer''.
Thus we would like to compose this constant function with the unary successor function.

This is exactly the role of the function \texttt{(composeFunc 0 1)}. Here is a quite simple proof of \texttt{const0\_NIsPR}.

@@

We have already proven that \texttt{Nat.add} is primitive recursive. The following alternative proof, --- more detailed  ---, 
shows how to search and apply lemmas from
the \texttt{Ackermann} library.

Let us look for some lemma which could help to prove a given  
recursive arithmetic binary function is primitive recursive.
